### 2015-09-23 todo.tex
man these are out of date, but not gonna fix them today

\input{header.tex}

@@

  \begin{itemize}
    \item Menger/Rothberger properties and games results
      \begin{itemize}
        \item Is there a slick characterization of $F\kmarkwin{2}\mengame{X}$ for regular/general spaces?
        \item Is $F\uparrow_{?}\mengame{X}$ or $F\uparrow_{?}\rothgame{X}$ a hereditary property under closed subsets for any type of limited information? (The Menger property is; is Rothberger?)
        \item Investigate Markov strategies for $S$ in $\rothgame{X}$ or $P$ in $\altrothgame{X}$.
        \item $S\kmarkwin{2}\rothgame{X}\Leftrightarrow S\kmarkwin{k}\rothgame{X}$?
        \item $S\kmarkwin{2}\rothgame{\oneptcomp{\omega_1}}$ or $S\kmarkwin{2}\rothgame{\oneptlind{\omega_1}}$?
        \item $F\kmarkwin{k}\kfillgame{\kappa} \Rightarrow F\kmarkwin{k}\mengame{\oneptlind{\kappa}}$?
        \item Would Lindelof scattered spaces have a $2$-Markov strategy in the Menger game?
      \end{itemize}
    \item Filling games
      \begin{itemize}
        \item Show/disprove $F\ktactwin{3}\sfillgame{J}$ implies $F\kmarkwin{3}\fillgame{J}$.
        \item Show/disprove $F\kmarkwin{2}\mengame{\oneptlind{\kappa}}$ implies $F\kmarkwin{2}\kfillgame{\kappa}$.
      \end{itemize}
    \item Search for a class of spaces where $K\ktactwin{2}\lfkpgame{X}$ characterizes metacompact (aka implies $K\tactwin\lfkpgame{X}$)
      \begin{itemize}
        \item Investigate the ladder space suggested by G.
        \item Try zero-dimensional.
      \end{itemize}
    \item Proximity Game
      \begin{itemize}
        \item Question: predetermined strategy for D on abs. proxmial space, does that imply predetermined strategy for O in con(X,H) for H compact.
        \item Is proximal game properties preserved under perfect maps? Or, compact proximal preserved under continuous.
        \item Alexandrof duplicate of unit interval: EC, not metrizable, what about Markov proximal?
      \end{itemize}
  \end{itemize}
\end{document}

>>>>

\input{header}

@@

  \begin{itemize}
    \item write these TODOs
  \end{itemize}
\end{document}
